---
title: "Missing data"
author: "Lovedeep Gondara"
date: "May 5, 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Contents

- Overview 
- Conventional imputation
- Modern imputation
- Loss to follow-up as a missing data problem
- Examples

## Overview

"A data point is said to be missing when no data value is stored for that variable in an observation".

## Overview

Missing data are a common occurence and can have serious consequences on analysis and inference.

## Overview

Missing data are a common occurence and can have serious consequences on analysis and inference.

## Overview

```{r, echo = FALSE}
height = c(175, 168, 170, 171, 169, 165, 165, 160, 190, 199)
weight = c(80, 68, 72, 75, 70, 65, 62, 60, 85, 90)
plot(weight,height)
```

## Overview

```{r, echo = FALSE}
height = c(175, 168, 170, 171, 169, 165, 165, 160, 190, 199)
weight = c(80, 68, 72, 75, 70, 65, 62, 60, 85, 90)
plot(weight,height)
abline(lm(height ~ weight))
```

## Overview

```{r, echo = FALSE}
height = c(175, 168, 170, 171, 169, 165, 165, 160, NA, NA)
weight = c(80, 68, 72, 75, 70, 65, 62, 60, 85, 90)
plot(weight,height,ylim=c(160,200))
abline(lm(height ~ weight))
```

## Overview

Missing data types

- Missing completely at random (MCAR)
- Missing at random (MAR)
- Missing not at random (MNAR)

## Overview

Missing completely at random (MCAR)




